---
title: "Plot interactions"
author: "Christophe Nicault"
date: '2022-05-12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


## Function interactive

```{r}

couples_graph <- function(data, col1, col2, n = 500){

  col1 <- sym(col1)
  col2 <- sym(col2)
  
  p <- data |> 
    sample_n(n) |> 
    ggplot(aes({{col1}}, {{col2}}, color = as.factor(target)))+
    geom_point(alpha = 0.7, size = 0.6)+
    scale_color_manual(values = c("0" = "#0477BF", "1" = "#D95B96")) +
    theme_light()

}


map2(all_couples$col1, all_couples$col2, ~couples_graph(train, .x, .y, n = 15000))

couples_graph_save(train, "f_02", "f_21", 500)

couples_graph(train, "f_02", "f_21", 500)
couples_graph(train, f_02, f_21, 500)
```


## function save on disk

```{r}

couples_graph_save <- function(data, col1, col2, n = 500){

  file_name = glue::glue("graph_{col1}_{col2}.png")
  subdir = col1
  
  col1 <- sym(col1)
  col2 <- sym(col2)
  
  p <- data |> 
    sample_n(n) |> 
    ggplot(aes({{col1}}, {{col2}}, color = as.factor(target)))+
    geom_point(alpha = 0.3, size = 0.3)+
    scale_color_manual(values = c("0" = "#0477BF", "1" = "#D95B96")) +
    labs(title = glue::glue("variable {col1} vs {col2}"))+
    theme_light()
  
  if(!file.exists(here::here("graphs", subdir))){
    dir.create(file.path(here::here("graphs"), subdir))
  }
  
  ggsave(here::here("graphs", subdir, file_name), p, device = "png", dpi = 300, width = 5, height = 5)

}
```

## function save on disk with jitter (for qualitative)

```{r}
couples_graph_jit_save <- function(data, col1, col2, n = 500, jit_width = 0.4, jit_height = 0.4){

  file_name = glue::glue("graph_{col1}_{col2}.png")
  subdir = col1
  
  col1 <- sym(col1)
  col2 <- sym(col2)
  
  p <- data |> 
    sample_n(n) |> 
    ggplot(aes({{col1}}, {{col2}}, color = as.factor(target)))+
    geom_jitter(alpha = 0.3, size = 0.1, width = jit_width, height = jit_height)+
    scale_color_manual(values = c("0" = "#0477BF", "1" = "#D95B96")) +
    labs(title = glue::glue("variable {col1} vs {col2}"))+
    theme_light()
  
  if(!file.exists(here::here("graphs", subdir))){
    dir.create(file.path(here::here("graphs"), subdir))
  }
  
  ggsave(here::here("graphs", subdir, file_name), p, device = "png", dpi = 150, width = 5, height = 5)

}


```

## Load and process data

```{r}

train <- read_csv(here::here("data", "train.csv"))


train <- train |> 
  mutate(letter_count = map_int(f_27, \(x) {length(unique(str_split(x, pattern = '')[[1]]))})) |> 
  separate(col = f_27, into = paste0("f_27_", seq(1, 10, 1)), sep = seq(1,10,1), remove = FALSE)
```

## Generate all plots for continuous variables

```{r}
all_cols <- c("f_00","f_01", "f_02", "f_03", "f_04", "f_05", "f_06", "f_19", "f_20", "f_21", "f_22", "f_23", "f_24", "f_25", "f_26", "f_28", "f_29", "f_30")

all_couples <- expand.grid(col1 = all_cols, col2 = all_cols) |> 
  filter(col1 != col2) |> 
  mutate(across(everything(), as.character))

walk2(all_couples$col1, all_couples$col2, ~couples_graph_save(train, .x, .y, n = 900000))
```

## Generate for f_29 et f_30 vs continuous

```{r}
col1 <- c("f_29", "f_30")
col2 <- c("f_00","f_01", "f_02", "f_03", "f_04", "f_05", "f_06", "f_19", "f_20", "f_21", "f_22", "f_23", "f_24", "f_25", "f_26", "f_28", "f_29", "f_30")

all_couples <- expand.grid(col1 = col1, col2 = col2, stringsAsFactors = FALSE) |> 
  filter(col1 != col2) |> 
  mutate(across(everything(), as.character))

walk2(all_couples$col1, all_couples$col2, ~couples_graph_jit_save(train, .x, .y, n = 900000, jit_width = 0.4, jit_height = 0))
```

## Generate for all qualitative vs qualitative

```{r}
col1 <- c("f_07","f_08", "f_09", "f_10", "f_11", "f_12", "f_13", "f_14", "f_15", "f_16", "f_17", "f_18", "f_27_1", "f_27_2", "f_27_3", "f_27_4", "f_27_5", "f_27_6", "f_27_7", "f_27_8", "f_27_9", "f_27_10", "f_29", "f_30")
col2 <- c("f_07","f_08", "f_09", "f_10", "f_11", "f_12", "f_13", "f_14", "f_15", "f_16", "f_17", "f_18", "f_27_1", "f_27_2", "f_27_3", "f_27_4", "f_27_5", "f_27_6", "f_27_7", "f_27_8", "f_27_9", "f_27_10", "f_29", "f_30")

all_couples <- expand.grid(col1 = col1, col2 = col2, stringsAsFactors = FALSE) |> 
  filter(col1 != col2) |> 
  mutate(across(everything(), as.character))

walk2(all_couples$col1, all_couples$col2, ~couples_graph_jit_save(train, .x, .y, n = 900000, jit_width = 0.4, jit_height = 0.4))
```

## Generate for all pseudo qualitative (integer but more likely categories) vs continuous

```{r}
col1 <- c("f_07","f_08", "f_09", "f_10", "f_11", "f_12", "f_13", "f_14", "f_15", "f_16", "f_17", "f_18")
col2 <- c("f_00","f_01", "f_02", "f_03", "f_04", "f_05", "f_06", "f_19", "f_20", "f_21", "f_22", "f_23", "f_24", "f_25", "f_26", "f_28")

all_couples <- expand.grid(col1 = col1, col2 = col2, stringsAsFactors = FALSE) |> 
  filter(col1 != col2) |> 
  mutate(across(everything(), as.character))

walk2(all_couples$col1, all_couples$col2, ~couples_graph_jit_save(train, .x, .y, n = 900000, jit_width = 0.4, jit_height = 0))
```

## Generate for all texte encoding vs continuous

```{r}


col1 <- c("f_27_1", "f_27_2", "f_27_3", "f_27_4", "f_27_5", "f_27_6", "f_27_7", "f_27_8", "f_27_9", "f_27_10")
col2 <- c("f_00","f_01", "f_02", "f_03", "f_04", "f_05", "f_06", "f_19", "f_20", "f_21", "f_22", "f_23", "f_24", "f_25", "f_26", "f_28", "f_29", "f_30")

all_couples <- expand.grid(col1 = col1, col2 = col2, stringsAsFactors = FALSE) |> 
  filter(col1 != col2) |> 
  mutate(across(everything(), as.character))

walk2(all_couples$col1, all_couples$col2, ~couples_graph_jit_save(train, .x, .y, n = 900000))
```

